manuscript_outline

### 2025-05-27 docs/manuscript/paper.Rmd
fig caps for paper.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(hatchR); library(tidyverse); library(patchwork)
```

@@

Morgan M. Sparks, Brian Leavell, Bryan M. Maitland
\newpage

@@

```{r}
# Brown 1975, Comparitive Biochemistry and Physicology Part A: Physiology
# https://www.sciencedirect.com/science/article/pii/030096297590033X

@@

p1 + p2
```

@@

| Class | Order | Genera | Species | Study |
|:----------------------|:------------|:------------|:------------|:-----------|
| Amphibia | Anura | *Lithobates* | *L. sylvaticus* | @moore1939 |
|  |  |  | *L. pipiens* |  |
|  |  |  | *L. clamitans* |  |
|  |  |  | *L. palustris* |  |
|  |  | *Ascaphus* | *A. truei* | @brown1975 |
|  | Urodela | *Ambystoma* | *A. gracile* | @brown1976 |
| Reptilia | Squamata | *Sceloporus* | *S. undulatus* |  @angilletta2000 |
|  |  | Podarcis | *P. mural*is | @vandamme1992 |
|  | Testudines | Mauremys | M. reevesii | @du2007 |
|  |  |  | 181 species | 141 studies in @while2018 |
| Insecta | Plecoptera | *Nemurella* | *N. pictetii* | @brittain1978, @elliott1984 |
|  |  | *Capnia* | *C. atra* | @brittain1984 |
|  |  | *Capnia* | *C. bifrons* | @elliott1986 |
|  |  | *Mesocapnia* | *M. oenone* | @brittain1984 |
|  |  | *Taeniopteryx* | *T. nebulosa* | @brittain1977 |
| Malacostraca | Decapoda | *Pontastacus* | *P. leptodactylus* | @aydin2004 |

@@

```{r}

@@

p2.1 <- ggplot() +
  geom_point(data = temperature_data, aes(x = dates, y = temperatures)) +
  geom_line(data = temperature_data, aes(x = dates, y = temperatures)) +
  geom_rect(data = froggy_hatch, aes(xmin = start, xmax = stop, ymax =index-.15, ymin = index-.5, fill = species)) +
  geom_label(data = froggy_hatch, aes(x = start + (stop - start) / 1.45, y = (index -0.325), label = days_to_develop)) +
  labs(x = "Date", y = "Temperature (°C)",
       title = "Development periods of four North American Frog Species") +
  scale_fill_manual(values = c("darkolivegreen4","deepskyblue4", "grey23",  "purple4"), name = "Species") +
  theme_classic() +
  theme(legend.position = c(0.75, 0.25))

```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(hatchR)
library(tidyverse)
library(patchwork)
```

@@

Morgan M. Sparks^1^, Brian Leavell^2^, Bryan M. Maitland^1^

^1^Rocky Mountain Research Station, U.S. Forest Service, Boise, Idaho

^2^ Brian's deets here

\newpage

@@

```{r, fig.align = 'center', fig.cap="Custom hatching phenology model for western tailed frogs (Ascaphus truei).Panel A represents the model fit and raw data used to generate the effective value model and panel B are the effective values for daily temperatures between 6 and 20 °C. A dashed line with a 0.01 increase for every degree increase in included for reference."}
# Brown 1975, Comparitive Biochemistry and Physicology Part A: Physiology
# https://www.sciencedirect.com/science/article/pii/030096297590033X

@@

p1 + p2 + plot_annotation(tag_levels = 'A')
```

@@

| Class | Order | Genera | Species | Study |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia | Anura | *Lithobates* | *L. sylvaticus* | @moore1939 |
|  |  |  | *L. pipiens* |  |
|  |  |  | *L. clamitans* |  |
|  |  |  | *L. palustris* |  |
|  |  | *Ascaphus* | *A. truei* | @brown1975 |
|  | Urodela | *Ambystoma* | *A. gracile* | @brown1976 |
| Reptilia | Squamata | *Sceloporus* | *S. undulatus* | @angilletta2000 |
|  |  | Podarcis | *P. mural*is | @vandamme1992 |
|  | Testudines | Mauremys | M. reevesii | @du2007 |
|  |  |  | 181 species | 141 studies in @while2018 |
| Insecta | Plecoptera | *Nemurella* | *N. pictetii* | @brittain1978, @elliott1984 |
|  |  | *Capnia* | *C. atra* | @brittain1984 |
|  |  | *Capnia* | *C. bifrons* | @elliott1986 |
|  |  | *Mesocapnia* | *M. oenone* | @brittain1984 |
|  |  | *Taeniopteryx* | *T. nebulosa* | @brittain1977 |
| Malacostraca | Decapoda | *Pontastacus* | *P. leptodactylus* | @aydin2004 |

: Sources for effective value parameterizations using `fit_model()` in hatchR. Represented are a broad range of taxa and some review studies which include numerous putative sources.

@@

Frog example Moore 1939.

```{r, fig.align = 'center', fig.cap="Custom hatch timing models developed for four North American frog species. Models are parameterized from Moore 1939 and phenology is predicted using a randomly generated temperature regime with mean 16 °C."}

@@

p2.1 <- ggplot() +
  geom_point(data = temperature_data, aes(x = dates, y = temperatures)) +
  geom_line(data = temperature_data, aes(x = dates, y = temperatures)) +
  geom_rect(data = froggy_hatch, aes(xmin = start, xmax = stop, ymax =index-.15, ymin = index-.5, fill = species)) +
  geom_label(data = froggy_hatch, aes(x = start + (stop - start) / 1.45, y = (index -0.325), label = days_to_develop)) +
  labs(x = "Date", y = "Temperature (°C)") +
  scale_fill_manual(values = c("darkolivegreen4","deepskyblue4", "grey23",  "purple4"), name = "Species") +
  theme_classic() +
  theme(legend.position = c(0.75, 0.25))

p2.1
```
